---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# Vogelnamen

<!-- badges: start -->
<!-- badges: end -->

This is a data package that contains BirdNET codes, species, family and order - common and scientific - in german and english all in one place. Also includes breeding ranges (biogeographical scale).


## Installation

You can install the development version of Vogelnamen from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("OekoFor/Vogelnamen")
```

## Available Datasets

```{r available_datasets}
library(Vogelnamen)

ls.str("package:Vogelnamen") |> print(max.level=0)
```


## Skim Datasets

### birdnet codes

```{r}
# For column descriptions of the datasets see
# ?birdnet_codes_v23
```


```{r example_birdnetcodes}
skimr::skim(birdnet_codes_v24)
```

### breeding range codes

```{r example_breedingrange}
skimr::skim(breedingrange_codes)
```

```{r breedingranges}

breedingrange_codes |> 
  knitr::kable()
```



## Data sources

Missing 😙
